Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2015-05-18 Paper/paper.tex
minor change
added first figures

\documentclass[aps,prl,amsmath,floats,floatfix, twocolumn,
superscriptaddress,nofootinbib,showpacs]{revtex4-1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Systematic bias in recovered parameters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Advanced LIGO searches and parameter estimation efforts aimed at binaries 
containing NS and stellar-mass BHs are poised to use waveform models that do not
include the effects of the NS tidal deformability. While this is not expected to
be the dominant source of error at low SNRs, it will likely introduce a
systematic bias in the physical parameters that we recover from GW observations.
In this section, we study the impact of the same for binaries where the BH spins
are aligned to the orbital angular momentum.

>>>>

\documentclass[aps,prd,amsmath,floats,floatfix, twocolumn,
superscriptaddress,nofootinbib,showpacs]{revtex4-1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Systematic bias in recovered parameters}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[h]
\centering 
\textbf{Without BH-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TN_chirpMassBias_vs_SNR_q23.pdf}\\ 
\textbf{Without NS-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TT_chirpMassBias_vs_SNR_q23.pdf}%\quad
\caption{These figures show the unfaithfulness of the two EOB models we consider
in this paper against NR, with the top panel corresponding to SEOBNRv1 and the bottom panel to
SEOBNRv2. Note that the SEOBNRv1 model does not include component spins
higher than $+0.6$, we cannot compute its faithfulness in that region of binary parameter space.
We find that both models have high agreement with NR for smaller mass-ratios 
and/or small spin magnitudes. The SEOBNRv1 model significantly deviates from the NR 
waveform when the spin of the primay black hole reaches $\sim +0.6$ for $q=3$, while
SEOBNRv2 appears to be unfaithful to NR when \textit{both} black holes have high spin 
magnitudes, especially when both spins are aligned with the orbital angular momentum.
}
\label{fig:SEOB_unfaith_TotalMass_Spin1z_Spin2z}
\end{figure*}
% 
\begin{figure*}[h]
\centering    
\textbf{Without BH-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TN_EtaBias_vs_SNR_q23.pdf}\\ 
\textbf{Without NS-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TT_EtaBias_vs_SNR_q23.pdf}%\quad
\caption{These figures show the unfaithfulness of the two EOB models we consider
in this paper against NR, with the top panel corresponding to SEOBNRv1 and the bottom panel to
SEOBNRv2. Note that the SEOBNRv1 model does not include component spins
higher than $+0.6$, we cannot compute its faithfulness in that region of binary parameter space.
We find that both models have high agreement with NR for smaller mass-ratios 
and/or small spin magnitudes. The SEOBNRv1 model significantly deviates from the NR 
waveform when the spin of the primay black hole reaches $\sim +0.6$ for $q=3$, while
SEOBNRv2 appears to be unfaithful to NR when \textit{both} black holes have high spin 
magnitudes, especially when both spins are aligned with the orbital angular momentum.
}
\label{fig:SEOB_unfaith_TotalMass_Spin1z_Spin2z}
\end{figure*}
% 
\begin{figure*}[h]
\centering    
\textbf{Without BH-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TN_BHspinBias_vs_SNR_q23.pdf}\\ 
\textbf{Without NS-BH Templates}
\includegraphics[width=2\columnwidth]{plots/TT_BHspinBias_vs_SNR_q23.pdf}%\quad
\caption{These figures show the unfaithfulness of the two EOB models we consider
in this paper against NR, with the top panel corresponding to SEOBNRv1 and the bottom panel to
SEOBNRv2. Note that the SEOBNRv1 model does not include component spins
higher than $+0.6$, we cannot compute its faithfulness in that region of binary parameter space.
We find that both models have high agreement with NR for smaller mass-ratios 
and/or small spin magnitudes. The SEOBNRv1 model significantly deviates from the NR 
waveform when the spin of the primay black hole reaches $\sim +0.6$ for $q=3$, while
SEOBNRv2 appears to be unfaithful to NR when \textit{both} black holes have high spin 
magnitudes, especially when both spins are aligned with the orbital angular momentum.
}
\label{fig:SEOB_unfaith_TotalMass_Spin1z_Spin2z}
\end{figure*}
% 
\begin{figure*}[h]
\centering    
\includegraphics[width=2\columnwidth]{plots/TT_NSLambdaBias_vs_SNR_q23.pdf}
\caption{These figures show the unfaithfulness of the two EOB models we consider
in this paper against NR, with the top panel corresponding to SEOBNRv1 and the bottom panel to
SEOBNRv2. Note that the SEOBNRv1 model does not include component spins
higher than $+0.6$, we cannot compute its faithfulness in that region of binary parameter space.
We find that both models have high agreement with NR for smaller mass-ratios 
and/or small spin magnitudes. The SEOBNRv1 model significantly deviates from the NR 
waveform when the spin of the primay black hole reaches $\sim +0.6$ for $q=3$, while
SEOBNRv2 appears to be unfaithful to NR when \textit{both} black holes have high spin 
magnitudes, especially when both spins are aligned with the orbital angular momentum.
}
\label{fig:SEOB_unfaith_TotalMass_Spin1z_Spin2z}
\end{figure*}
% 
% 
Advanced LIGO searches and parameter estimation efforts aimed at binaries 
containing NS and stellar-mass BHs are poised to use waveform models that do not
include the effects of the NS tidal deformability. While this is not expected to
be the dominant source of error at low SNRs, it will likely introduce a
systematic bias in the physical parameters that we recover from GW observations.
In this section, we study the impact of the same for binaries where the BH spins
are aligned to the orbital angular momentum.
